Machine learning topological phases in real space

### 2020-07-23 07_paper/supplementary.tex
Beta of paper finished. Waiting Griffith's reply.

\begin{figure}
\centering
\subfigure[]{\label{cumulative_entropy_ssh1_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_140_6561/plot_cumulative_feature_importances}}
\subfigure[]{\label{cumulative_entropy_ssh1_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_180_6561/plot_cumulative_feature_importances}}
\subfigure[]{\label{cumulative_entropy_ssh1_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_220_6561/plot_cumulative_feature_importances}}
\caption{Cumulative entropy distributions for higher lattice sizes in experiment 1. (a) Cumulative entropy distribution for 70 unit cells. (b) Cumulative entropy distribution for 90 unit cells. (c) Cumulative entropy distribution for 110 unit cells. The two visible leaps in the cumulative entropy distributions shown above occur at regions corresponding to the lattice sites $S_1$ in the case with 50 unit cells.}
\label{cdf1}
\end{figure}

\begin{figure}
\centering
\subfigure[]{\label{cumulative_entropy_ssh2_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_140_6561/plot_cumulative_feature_importances}}
\subfigure[]{\label{cumulative_entropy_ssh2_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_180_6561/plot_cumulative_feature_importances}}
\subfigure[]{\label{cumulative_entropy_ssh2_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_220_6561/plot_cumulative_feature_importances}}
\caption{Cumulative entropy distributions for higher lattice sizes in experiment 2. (a) Cumulative entropy distributions for 70 unit cells. (b) Cumulative entropy distributions for 90 unit cells. (c) Cumulative entropy distributions for 110 unit cells. Here the leaps in the cumulative entropy distributions are less pronounced than in experiment 1, but still noticeable. The three visible leaps occur at regions corresponding to the lattice sites $S_2$ in the case of 50 unit cells.}
\label{cdf2}
\end{figure}

>>>>

\begin{figure}
\centering
\subfigure[]{\label{cumulative_entropy_ssh1_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_140_6561/plot_cumulative_feature_importances}}
\subfigure[]{\label{cumulative_entropy_ssh1_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_180_6561/plot_cumulative_feature_importances}}
\subfigure[]{\label{cumulative_entropy_ssh1_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_220_6561/plot_cumulative_feature_importances}}
\caption{Cumulative entropy distributions for higher lattice sizes in experiment 1. (a) Cumulative entropy distribution for 70 unit cells. (b) Cumulative entropy distribution for 90 unit cells. (c) Cumulative entropy distribution for 110 unit cells.}
\label{cdf1}
\end{figure}

\begin{figure}
\centering
\subfigure[]{\label{cumulative_entropy_ssh2_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_140_6561/plot_cumulative_feature_importances}}
\subfigure[]{\label{cumulative_entropy_ssh2_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_180_6561/plot_cumulative_feature_importances}}
\subfigure[]{\label{cumulative_entropy_ssh2_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_220_6561/plot_cumulative_feature_importances}}
\caption{Cumulative entropy distributions for higher lattice sizes in experiment 2. (a) Cumulative entropy distributions for 70 unit cells. (b) Cumulative entropy distributions for 90 unit cells. (c) Cumulative entropy distributions for 110 unit cells.}
\label{cdf2}
\end{figure}
